---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
```
# psketti <img src ="img/psketti_hex2.png" align ="right" width="120"/>
   


psketti is a package for generating investigatory plots and tables for Rasch Analysis.
Models should first be estimated using eRm, psketti then pskettifies your Rasch data
and produces outputs using ggplot2.    

## Installation
```{r, eval=FALSE, results='hide'} 
devtools::install_github("SBGalvin/psketti") # install
```
## Loading
Loading psketti will produce the below startup message. If any of the dependencies are already loaded, psketti will tell you. If the dependencies are not installed at the time of the loading, psketti will tell you which ones to install. 
```{r, warning=FALSE, error=FALSE, message=FALSE}
library(eRm)
library(psketti)
```

```
-----------------------------------------------------
Loading psketti v 0.1.0
Beta Software !!!!


Dependencies:
	eRm		 (1.0.2) already loaded
	dplyr		 (1.0.4) already loaded
	ggplot2		 (3.3.3) loaded by psketti
	viridis		 (0.5.1) loaded by psketti


please install any NOT INSTALLED dependencies using:
install.packages('dependency')
-----------------------------------------------------
```

## Investigate Item Response Functions - Dichotomous Rasch Model
### 1.1 Prepare data
```{r IRF}


data("FakeData") # load data
# restructure fake data
Fake_Data_scores <- reshape(FakeData[, c("ID", "Item", "X")],
                           timevar = "Item",
                           idvar = "ID",
                           direction = "wide")
# for eRm new names
names(Fake_Data_scores) <- c("ID",
                             paste0("i",
                                    sprintf(fmt  = "%02d", 1:23)))

row.names(Fake_Data_scores) <- Fake_Data_scores$ID
Fake_Data_scores$ID <- NULL

fake_rm   <- RM(Fake_Data_scores) # Estimate Rasch model
```

### 1.2 pskettify your data
Convert your data into a format for psketti to use. Select confidence levels for empirical class interval values for empirical Item Characteristic Curves (ICC), and set the minimum and maximum x axis values for the Rasch Item Response Function (IRF).
```{r IRFobject}
psk_data <-pskettify(eRm.obj = fake_rm, conf.level = .95, Theta.lwr = -6, Theta.upr = 6)
```    

### 1.3 Plot Rasch IRF curves
Plot IRFs for individual items with empirical ICC, and class interval averages with confidence intervals
```{r IRFcolour}
# plot ICC for one item
psk_1_present <- psketto(psk_data,
                         style = "present",
                         item = "i01",
                         item.label = "i01")
psk_1_present
```


```{r IRFBW}
psk_1_print <- psketto(psk_data,
                       style = "print",
                       item = "i01",
                       item.label = "i01")
psk_1_print
```

...or use psketti() to plot ICC for all plots. `psketti()` objects printed to the 
console will print suggestions for how to call a plot.

```{r IRFmulti}
# plot ICC for one item
psk_IRF <- psketti(psk_data)
psk_IRF
```

```{r IRFmulti2}
psk_IRF$Plot.List[["i06"]][[1]]
```

```{r IRFmulti3}
psk_IRF$Plot.List[["i12"]][[1]]
```

### 1.4 Item Fit statistics

Produce a table of item fit statistics as per eRm
```{r Itmfit}
itemFit_psk <- item_fit_table(fake_rm)

# round ouput to 2 places
itemFit_psk[, -1] <- round(itemFit_psk[, -1], 2)
itemFit_psk
```



Produce Plot of infit and outfit statistics
```{r MSQ1}
psketti_msq(x = itemFit_psk)
```


### 1.5 Investigate distractor options

```{r SAtables}
# response option categories
r_o <- factor(sort(unique(FakeData$K)), levels = sort(unique(FakeData$K)), ordered = TRUE)
tlt_data <- tabliatelle(x = FakeData, ID = "ID", Item = "Item", K = "K", 
                        response_options = r_o, eRm.obj = fake_rm)
tlt_data
```

### 1.6 Plot the distractor empirical ICC against the dichotomous Rasch ICC
```{r Spagcol}
# multiple plots
spag_plot <- psketti_distractor(ID = "ID",              # set ID column
                                Item = "Item",          # set Item column
                                K= "K",                 # Set resp categories 
                                x = FakeData,           # select data
                                eRm.obj = fake_rm,      # select eRm object
                                response_options = r_o, # set resp options
                                p.style = "present")    # set plotting style
 

spag_plot$Plot.List[['i01']][[1]] # plot item 1
```


### 1.7 Print a score report
```{r ScrReport}
K_opt <- factor(LETTERS[1:5], levels = LETTERS[1:5], ordered = TRUE)
score_report <- ingrediente(x = FakeData,
                            Item = "Item",
                            ID = "ID",
                            Score = "X",
                            K = "K",
                            K_options = K_opt,
                            Index = "Index")

# show score report for values with a total score <= 1
score_report[score_report$total_score <= 1, ]
```


## 2 Rasch Partial Credit Model
### 2.1 Prepare data
```{r PCM}
data("FakePCMData")

F2           <- FakePCMData
rownames(F2) <- F2$ID
F2$ID        <- NULL

fake_pcm <- PCM(F2)
```

### 2.2 pskettify
```{r PCMpsk}
psk_pcm <- pskettify(eRm.obj = fake_pcm) # pskettify
psk_pcm 
```

### 2.3  Plot PCM ICC
```{r PCMplot1}
psk_no_facet <- psketto(pskettified_data = psk_pcm, item = "i01", item.label = "i01")
psk_no_facet
```

### 2.3 Plot PCM ICC with facet curves
```{r PCMplot2}
psk_facet <- psketto(pskettified_data = psk_pcm, item = "i01", item.label = "i01", facet_curves = TRUE)
psk_facet
```

### 2.4 plot all ICC
By default `psketti()` produces faceted plots for partial credit models
```{r PCMplot3}
print_facet <- psketti(pskettified_data = psk_pcm)
print_facet$Plot.List[['i01']][[1]] # output
```

However, you can turn off this behaviour by using the `Force_no_facet=True` argument.
```{r PCMplot4}
print_no_facet <- psketti(pskettified_data = psk_pcm, p.empICC = FALSE, Force_no_facet = TRUE)
print_no_facet$Plot.List[['i02']][[1]]
```

### 2.5 PCM item fit
Item fit statistic.
```{r PCMitm}
fake_ifit <- item_fit_table(eRm.obj = fake_pcm)

# round ouput to 2 places
fake_ifit[, -c(1, 2)] <- round(fake_ifit[, -c(1, 2)], 2)
fake_ifit
```

Infit and Outfit MSQ plot.
```{r PCMMSQ}

psketti_msq(x = fake_ifit)
```



