---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# psketti <img src ="img/psketti_hex2.png" align ="right" width="120"/>
   

## Overview
psketti is a package for generating investigatory plots and tables for Rasch Analysis.
Models should first be estimated using eRm, psketti then pskettifies your Rasch data
and produces outputs using ggplot2.

## Installation
```{r noInstall, echo = TRUE, eval=FALSE} 
devtools::install_github("SBGalvin/psketti")
```


## Investigate Item Response Functions - Dichotomous Rasch Model
### (0) Prepare data
```{r IRF}
library(eRm)
library(psketti)

data("FakeData") # load data
# restructure fake data
Fake_Data_scores <- reshape(FakeData[, c("ID", "Item", "X")],
                           timevar = "Item",
                           idvar = "ID",
                           direction = "wide")
# for eRm new names
names(Fake_Data_scores) <- c("ID",
                             paste0("i",
                                    sprintf(fmt  = "%02d", 1:23)))

row.names(Fake_Data_scores) <- Fake_Data_scores$ID
Fake_Data_scores$ID <- NULL

fake_rm   <- RM(Fake_Data_scores) # Estimate Rasch model
```

### (1) pskettify your data
Convert your data into a format for psketti to use. Select confidence levels for empirical class interval values for empirical Item Chracteristic Curves (ICC), and set the minimum and maximum x axis values for the Rasch Item Response Function (IRF).
```{r IRFobject}
psk_data <-pskettify(eRm.obj = fake_rm, conf.level = .95, Theta.lwr = -6, Theta.upr = 6)
```    

### (2) Plot Rasch IRF curves
Plot IRFs for individual items with empirical ICC, and class interval averages with confidence intervals
```{r IRFcolour}
# plot ICC for one item
psk_1_present <- psketto(psk_data,
                         style = "present",
                         item = "i01",
                         item.label = "i01")
psk_1_present
```


```{r IRFBW}
psk_1_print <- psketto(psk_data,
                       style = "print",
                       item = "i01",
                       item.label = "i01")
psk_1_print
```

...or use psketti() to plot ICC for all plots. `psketti()` objects printed to the 
console will print suggestions for how to call a plot.

```{r IRFmulti}
# plot ICC for one item
psk_IRF <- psketti(psk_data)
psk_IRF
```

```{r IRFmulti2}
psk_IRF$Plot.List[["i06"]][[1]]
```

```{r IRFmulti3}
psk_IRF$Plot.List[["i12"]][[1]]
```

### (3) Item Fit statistics

Produce a table of item fit statistics as per eRm
```{r Itmfit}
itemFit_psk <- item_fit_table(fake_rm)
itemFit_psk
```

Produce Plot of infit and outfit statistics
```{r MSQ1}
psketti_msq(x = itemFit_psk)
```


### (4) Investigate distractor options

```{r SAtables}
# response option categories
r_o <- factor(sort(unique(FakeData$K)), levels = sort(unique(FakeData$K)), ordered = TRUE)
tlt_data <- tabliatelle(x = FakeData, ID = "ID", Item = "Item", K = "K", 
                        response_options = r_o, eRm.obj = fake_rm)
tlt_data
```

### (5) Plot the distractor empirical ICC against the dichotomous Rasch ICC
```{r Spagcol}
# multiple plots
spag_plot <- psketti_distractor(ID = "ID",              # set ID column
                                Item = "Item",          # set Item column
                                K= "K",                 # Set resp categories 
                                x = FakeData,           # select data
                                eRm.obj = fake_rm,      # select eRm object
                                response_options = r_o, # set resp options
                                p.style = "present")    # set plotting style
 

spag_plot$Plot.List[['i01']][[1]] # plot item 1
```


### (6) Plot a score report
```{r ScrReport}
K_opt <- factor(LETTERS[1:5], levels = LETTERS[1:5], ordered = TRUE)
score_report <- ingrediente(x = FakeData,
                            Item = "Item",
                            ID = "ID",
                            Score = "X",
                            K = "K",
                            K_options = K_opt,
                            Index = "Index")

# show score report for values with a total score <= 5
score_report[score_report$total_score <= 1, ]
```


## Rasch Partial Credit Model

```{r PCM}
data("FakePCMData")

F2           <- FakePCMData
rownames(F2) <- F2$ID
F2$ID        <- NULL

fake_pcm <- PCM(F2)
```

```{r PCMpsk}
psk_pcm <- pskettify(eRm.obj = fake_pcm) # pskettify
psk_pcm 
```

```{r PCMplot1}
psk_no_facet <- psketto(pskettified_data = psk_pcm, item = "i01", item.label = "i01")
psk_no_facet
```

```{r PCMplot2}
psk_facet <- psketto(pskettified_data = psk_pcm, item = "i01", item.label = "i01", facet_curves = TRUE)
psk_facet
```

By default `psketti()` produces faceted plots for partial credit models
```{r PCMplot3}
print_facet <- psketti(pskettified_data = psk_pcm)
print_facet$Plot.List[['i01']][[1]] # output
```

However, you can turn off this behaviour by using the `Force_no_facet=True` argument.
```{r PCMplot4}
print_no_facet <- psketti(pskettified_data = psk_pcm, p.empICC = FALSE, Force_no_facet = TRUE)
print_no_facet$Plot.List[['i02']][[1]]
```

```{r PCMitm}
fake_ifit <- item_fit_table(eRm.obj = fake_pcm)
```


```{r PCMMSQ}

psketti_msq(x = fake_ifit)
```



